


---
title: 'The Anatomy of a Plot'
subtitle: "moving from ggplot2 to highcharter"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
    css: ~/Documents/R/dashboard_source_folder/css/starlight_css.css
    theme: bootstrap
    
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = FALSE) # always echo=FALSE for dashboards. No need to show off. you can include source code if you want
# bc you set echo to false, you don't actually need include=FALSE, message=FALSE, or warning=FALSE in the 
# chunk "preamble" (can I call it that? if it's called something else can I still call it that?) 
library(flexdashboard) # dashboards!
library(highcharter)   # for interactive plots
library(DT)            # for search/filter/downloadable tables
library(tidyverse)     # doi
options(scipen=999)    # keep scientific notation turned off
#source('dashboard_source_folder/R/file_export_for_dashboards.R')

```

<div class="footer">
  <p> NYR 2022 | Malorie Hughes | maloriejhughes@gmail.com | github.com/maloriejhughes </p>
</div>
  
  
Slides {data-orientation="columns"}
=====================================

Column {data-height=800}
-------------------------------------

```{r,dpi=240}
knitr::include_url('Highcharter_Slides.html', height="850px")
```



  
Bars & Columns {data-orientation="columns"}
=====================================

- first: the plot set up


- labeled image of names of different parts of the plot that we will modify (legend, names, fill opacity, color, title, xaxis title/tic marks/min/max, hover, grid lines, themes ) 

- labeling the bars through hover text

- group by vs add series

- names in legend

- opacity

- labeled image of code that controls the different parts of the plot,  side by side ggplot and highcharter


  
Lines  {data-orientation="columns"}
=====================================


- show in legend = false

- markers radius

- time x-axis

- starting with blank plot when you have many groups and want to allow specific comparisons

- zoom



Bonus: super fancy  {data-orientation="columns"}
=====================================

vertical and horizontal lines


line color based on y-value (conditional colors)

